The Astropy Project

### 2017-11-12 main.tex
keywords
time section

%% Keywords should appear after the \end{abstract} command.
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{}

@@

\subsection{Time}
\label{sec:time}

\inlinecomment{Tom, Marten?}

\inlinecomment{SCO}{Q: does it make sense to refer forward to FITS support, even though it is 3.0?-- If you want to say something add it to the future section, but I'd say no.}

Time and date functionality, especially those relevant to astronomy, are dealt by the \package{Time} package.  The package was described in detail in \cite{astropy}.  The \package{Time} package is currently built on ERFA \citep{erfa}, which replicates the functionality of SOFA \cite{sofa} but is licensed under a three-clause BSD license.

@@

\inlinecomment{SMC: Can a brief description of each code be added?}
\begin{longrotatetable}
  \begin{deluxetable*}{ccccc}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:registry}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
      \startdata
        \input{registry.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}

>>>>

% Adrian PW: how are there still no software keywords in AAS journals?!?
\keywords{
    Astrophysics - Instrumentation and Methods for Astrophysics
    ---
    methods: data analysis
    ---
    methods: miscellaneous
}

@@

\subsection{Time}
\label{sec:time}
% Tom, Marten?
% edited by Adrian PW

The \package{astropy.time} subpackage focuses on supporting time scales (e.g.,
UTC, TAI, UT1) and time formats (e.g., Julian date, modified Julian date) that
are commonly used in astronomy, for example, to calculate barycentric
corrections or sidereal times.
The core functionality is currently built on the ERFA (\citealt{erfa}) C
library, which replicates the Standards of Fundamental Astronomy (SOFA;
\citealt{sofa}) but is licensed under a three-clause BSD license.
The package was described in detail in \cite{astropy} and thus, in what follows,
we only highlight significant changes or new features.

\begin{description}
    \item[TODO] todo...
    \item[TODO] todo...
\end{description}

@@

\inlinecomment{SMC}{Can a brief description of each code be added?}

\begin{longrotatetable}
  \begin{deluxetable*}{ccccc}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:registry}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
      \startdata
        \input{registry.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}
